Gammapy: A Python package for gamma-ray astronomy

### 2023-03-22 src/ms-review.tex
Fix typos
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

With the public availability of the \gadf format specifications and the
\gammapy package, some experiments started to make limited subsets of
their \gammaray data publicly available for testing and validating
\gammapy. For example, the \hess collaboration released a limited test
dataset (about 50 hours of observations taken between 2004 and 2008)
based on the \gadf DL3 format \citep{HESS_DR1}. This data release served
as a basis for validation of open analysis tools, including \gammapy 
\cite[see e.g.][]{Mohrmann2019}. Two observations of the Crab nebula have been
 released by the \magic collaboration~\citep{magic_performance}, using which a
joint analysis across different gamma-ray instruments was first demonstrated in ~\cite{joint_crab}.
The \hawc collaboration also released
a limited test dataset of the Crab Nebula, which was used to validate
the \gammapy package in \cite{Olivera2022}.
The increased availability of public data that followed the definition of
a common data format, and the development of \gammapy as a community-driven open software,
led the way toward a more open science in the very-high-energy \gammaray Astronomy domain.
In future CTAO will be an open observatory committed to follow the FAIR
(Findable, Accessible, Interoperable and Reusable) principles \citep{FAIR16, FAIR22} 
that define the key requirements for open science.

>>>>

With the public availability of the \gadf format specifications and the
\gammapy package, some experiments started to make limited subsets of
their \gammaray data publicly available for testing and validating
\gammapy. For example, the \hess collaboration released a limited test
dataset (about 50 hours of observations taken between 2004 and 2008)
based on the \gadf DL3 format \citep{HESS_DR1}. This data release served
as a basis for validation of open analysis tools, including \gammapy 
\cite[see e.g.][]{Mohrmann2019}. Two observations of the Crab nebula have been
 released by the \magic collaboration~\citep{magic_performance}, using which a
joint analysis across different gamma-ray instruments was first demonstrated in ~\cite{joint_crab}.
The \hawc collaboration also released
a limited test dataset of the Crab Nebula, which was used to validate
the \gammapy package in \cite{Olivera2022}.
The increased availability of public data, that followed the definition of
a common data format, and the development of \gammapy as a community-driven open software
led the way toward a more open science in the very-high-energy \gammaray astronomy domain.
In future CTAO will be an open observatory committed to follow the FAIR
(Findable, Accessible, Interoperable and Reusable) principles \citep{FAIR16, FAIR22} 
that define the key requirements for open science.
